We take security seriously. Responsible reporting and disclosure of security vulnerabilities is important for the protection and privacy of our users. If you discover any security vulnerabilities, please follow these guidelines.

Published security advisories are available on our \href{https://github.com/KillianLucas/open-interpreter/security/advisories}{\texttt{ Git\+Hub Security Advisories}} page.

To report a vulnerability, please draft a \href{https://github.com/KillianLucas/open-interpreter/security/advisories/new}{\texttt{ new security advisory on Git\+Hub}}. Any fields that you are unsure of or don\textquotesingle{}t understand can be left at their default values. The important part is that the vulnerability is reported. Once the security advisory draft has been created, we will validate the vulnerability and coordinate with you to fix it, release a patch, and responsibly disclose the vulnerability to the public. Read Git\+Hub\textquotesingle{}s documentation on \mbox{[}privately reporting a security vulnerability\mbox{]} for details.

Please do not report undisclosed vulnerabilities on public sites or forums, including Git\+Hub issues and pull requests. Reporting vulnerabilities to the public could allow attackers to exploit vulnerable applications before we have been able to release a patch and before applications have had time to install the patch. Once we have released a patch and sufficient time has passed for applications to install the patch, we will disclose the vulnerability to the public, at which time you will be free to publish details of the vulnerability on public sites and forums.

If you have a fix for a security vulnerability, please do not submit a Git\+Hub pull request. Instead, report the vulnerability as described in this policy. Once we have verified the vulnerability, we can create a \mbox{[}temporary private fork\mbox{]} to collaborate on a patch.

We appreciate your cooperation in helping keep our users safe by following this policy. 